A Formal Verification Framework for Smart Contracts Based on Symbolic Execution

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
entrypoint relation syntax update

  (%create -> %bid) with (auction_open = true)  
       and (Amount > pre_Balance) 
       and get_contract (unit, highest_bidder) = 
           Some (c: contract unit)
  | (%create  -> %close) with (auction_open = true) 
       and (Sender = contract_owner)
       and get_contract (unit, contract_owner) = 
          Some (c: contract unit)
  | (%bid -> %bid) with (Amount > pre_Balance) 
       and get_contract (unit, highest_bidder) = 
          Some (c: contract unit)
  | (%bid -> %close) with (Sender = contract_owner) 
       and get_contract (unit, contract_owner) = 
            Some (c: contract unit)
  | not (%close -> %bid)
  | not (%close -> %close)
\end{lstlisting}

@@

     and (s = 'XTZ-USD') 
     and (Now - t >= 0)  
     and (Now - t < maxDelay)  

@@

    and get_contract (pair string (contract pair 

>>>>

  (%create -> %bid) with (auction_open = true)  
       && (Amount > pre_Balance) 
       && get_contract (unit, highest_bidder) = 
           Some (c: contract unit)
  | (%create  -> %close) with (auction_open = true) 
       && (Sender = contract_owner)
       && get_contract (unit, contract_owner) = 
          Some (c: contract unit)
  | (%bid -> %bid) with (Amount > pre_Balance) 
       && get_contract (unit, highest_bidder) = 
          Some (c: contract unit)
  | (%bid -> %close) with (Sender = contract_owner) 
       && get_contract (unit, contract_owner) = 
            Some (c: contract unit)
  | not (%close -> %bid)
  | not (%close -> %close)
\end{lstlisting}

@@

     && (s = 'XTZ-USD') 
     && (Now - t >= 0)  
     && (Now - t < maxDelay)  

@@

    && get_contract (pair string (contract pair 
